Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-02 icdm/submission/includes/related_work.tex
parallelization by the use of caching updated

\section{Related Work}
Due to the popularity of the SGM, a lot of research went into optimizing it. This research can be divided into two categories, optimization of the throughput and the optimization of the algorithm's accuracy. The latter was achieved by allowing words to have multiple meanings, also called context-sensitive word embedings. For our work, the optimization of the throughput is of big interest while the semantic optimization is aimed at giving the reader a more holistic comprehension of the possible research directions.
This subsection will first give an overview of the optimization of the throughput and then present one paper that focused on context-sensitive word embeddings.

In the original model, the optimization is done with Stochastic Gradient Descent (SGD), which is a sequential algorithm. This process does not favor parallelization. To deal with this specific problem Mikolov et al.\cite{mikolov2} used a Hogwild tree proposed by Recht et al.\cite{hogwild}. The approach is to allow multiple threads to access a shared memory, in this case, the single model. In the original SGM, the threads are constructed as follows: at the beginning of training, the dataset is split into $N$ evenly sized chunks and each of these chunks will be processed by a one thread. The threads run parallel and have access to the shared memory. Therefore, overwriting errors are bound to happen. According to Recht et al.\cite{hogwild} the overwriting errors won't lead to a significant accuracy loss if the data is sparse enough. But in the case of NLP, the problem seems to be a bit more significant, and especially for word embedding, as many words share the same context words. There were several attempts at solving this issue, and we are going to cover a few of them in the following subsubsections.

\paragraph{Parallelization by the use of caching}
This idea was proposed by Vuurens et al. \cite{efficient}. The architecture used here is the basic skip gram model with a hierarchical softmax. The general idea is to cache the most frequently used nodes of the binary tree used to memorize the probability distribution and update them on the shared single model after a certain number of seen words (the paper used the number 10). The paper produced interesting results as they managed to decrease execution time by increasing the number of cores used for the calculation. This is very powerful because in the original implementation the execution time regressed after using more than 8 cores. It seems to indicate that too much overwriting was happening, as the number of concurrent threads surpasses a certain threshold. This can be seen in Figure \ref{fig:efficient}, where c31 is the model proposed by Vuurens et al.\cite{efficient}. The model did not suffer any accuracy loss in comparison to the original SGM model.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.3]{images/cachingEfficiency.png}
\caption{Comparasion of the execution time in relation to the number of used cores \cite{efficient}}
\label{fig:efficient}
\end{figure}
This work proposes a very good way to parallelize the SGM, as in particular, it allows using more cores during the computation. As this approached focused on the Hierarchical softmax, in contrast to our work which used negative sampling, the next subsection covers optimizations of the Skip-Gram Model with negative sampling(SGNS).

>>>>

\section{Related Work}
In the original model, the optimization is done with Stochastic Gradient Descent (SGD), which is a sequential algorithm. This process does not favor parallelization. To deal with this specific problem Mikolov et al.\cite{mikolov2} used a Hogwild! approach proposed by Recht et al.\cite{hogwild}. The idea is to allow multiple threads to access a shared memory, in this case, the single model. In the original SGM, the threads are constructed as follows: at the beginning of training, the dataset is split into $N$ evenly sized chunks and each of these chunks will be processed by a one thread. The threads run parallel and have access to the shared memory. Therefore, overwriting errors are bound to happen. According to Recht et al.\cite{hogwild} the overwriting errors won't lead to a significant accuracy loss if the data is sparse enough. But in the case of NLP, the problem seems to be a bit more significant, and especially for word embedding, as many words share the same context words. There were several attempts at solving this issue, and optimize the throughput of the SGM.

\subsection{Parellelization by the use of caching}
This idea was proposed by Vuurens et al. \cite{efficient}. The architecture used here is the SGM with a hierarchical softmax.

The general idea is to cache the most frequently used weight vectors, and update the model after a certain number of seen training samples, while taking in consideration the changes that happend during these number of seen training samples (the paper used the number 10). The unfrequent weight vectors are handled as in the original paper, i.e updated in shared memory after each training sample. This technique  allows it to avoid collosision for the most frequent words, and the author therefore hoped to be able to increase the number of concurrent threads.The general idea is to cache the most frequently used nodes of the binary tree used to memorize the probability distribution and update them on the shared single model after a certain number of seen words. The paper produced interesting results as they managed to decrease execution time by increasing the number of cores used for the calculation. This is very powerful because in the original implementation the execution time regressed after using more than 8 cores. It seems to indicate that too much overwriting was happening, as the number of concurrent threads surpasses a certain threshold. This can be seen in Figure \ref{fig:efficient}, where c31 is the model proposed by Vuurens et al.\cite{efficient}. The model did not suffer any accuracy loss in comparison to the original SGM model.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.3]{images/cachingEfficiency.png}
\caption{Comparasion of the execution time in relation to the number of used cores \cite{efficient}}
\label{fig:efficient}
\end{figure}
This work proposes a very good way to parallelize the SGM, as in particular, it allows using more cores during the computation. As this approached focused on the Hierarchical softmax, in contrast to our work which used negative sampling, the next subsection covers optimizations of the Skip-Gram Model with negative sampling(SGNS).
